Fiber Collision Correction Method for BOSS Power Spectrum

### 2015-03-30 fc_paper/fc_paper.tex
First round of edits on the entire paper!

\section{Introduction} 
Through the millions of redshifts obtained through redshift surveys, cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements. These redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; CITE CITE) use fiber fed spectrographs.

@@

In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogues along with the redshift distribution of BOSS DR12 galaxies. The LasDamas mock catalogue, which is modeled after the SDSS LRG sample has a constant $\bar{n}(z)$ while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution.

% insert transition that mentions how the main clustering statistics we focus on in this paper is the Power Spectrum
In order to measure the power spectrum for these mock catalogues in our investigation, we use the standard \cite{Feldman:1994aa} (FKP) estimator. Throughout the paper we use the following formalisms from \cite{Feldman:1994aa}: 
\begin{equation} \label{eq:fkppk}
P({\bf k}) = <|F({\bf k})|^2> - \frac{(1+\alpha) \int d^3r \;\bar{n}({\bf r})w_{\mathrm{FKP}}^2({\bf r})} {\int d^3r \; \bar{n}^2({\bf r})w_{\mathrm{FKP}}^2({\bf r})},
\end{equation}  
where
\begin{equation}
F({\bf r}) = \frac{w_\mathrm{FKP}({\bf r}) [n_g({\bf r}) - \alpha n_r({\bf r})]} {[\int d^3r \; \bar{n}^2({\bf r})w_\mathrm{FKP}^2({\bf r})]^{\frac{1}{2}}} 
\end{equation}
and the second term represents the constant shot-noise contribution to the power due to the discrete density field of our galaxies. $n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalogue, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}: 
\begin{equation}
w_{\mathrm{FKP}} ({\bf r}) = \frac{1}{1+\bar{n}({\bf r}) P_0}
\end{equation}
where $P_0$ is the power spectrum amplitude at which the error is minimized. We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$.

@@

For LasDamas, QPM, and Tiling mock catalogues we use the above FKP estimator to measure the power spectrum in Figure \ref{fig:mockpk}. For the $P(k)$ in Figure \ref{fig:mockpk}, we do not apply the fiber-collisions to the catalogues. Therefore, there are no complications from using the exact formulation of Equation \ref{eq:fkppk}. When we calculate $P(k)$ for BOSS Data Release 12 data (\cmasscolor) in Figure \ref{fig:mockpk}, however, the systematic weights assigned to the galaxies that account for sector completeness, redshift failures, and fiber-collisions, 
\begin{equation} \label{eq:weight}
w_\mathrm{tot} = w_\mathrm{sys} (w_\mathrm{rf} + w_\mathrm{fc} -1), 
\end{equation}
must be taken account (\citealt{Anderson:2012aa, Beutler:2014aa}). Hence, instead of the galaxy density $n_g({\bf r})$ we use a weighted galaxy density $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$ and instead of $\alpha = N_{\mathrm{gal}}/N_\mathrm{ran}$ we use $\alpha ' = N'_\mathrm{gal}/N_\mathrm{ran}$ where $N'_\mathrm{gal} = \sum_\mathrm{gal} w_\mathrm{tot}$. For LasDamas and QPM, which have multiple realizations, we compute the sample variance of the power spectrum
\begin{equation} \label{eq:pk_var}
\Delta P (k)= \sqrt{\frac{1}{N_\mathrm{realization}} \sum\limits_i^{N_\mathrm{realization}} (P_i(k)- \overline{P(k)})^2 }. 
\end{equation}
$N_\mathrm{realization}$ is the total number of realizations (40 for LasDamas and 1000 for QPM) and $P_i(k)$ is the power spectrum for each realization. $\Delta P(k)$ is represented by the width of the $P(k)$ in Figure \ref{fig:mockpk}.

\begin{figure*}
\begin{center}
\includegraphics[scale=0.575]{fcpaper_dlos_dist.png}
\caption{Normalized distribution of $d_{\mathrm{LOS}}$ for Las Damas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogues. The normalized $d_{\mathrm{LOS}}$ distribution of BOSS DR12 is also plotted (\cmasscolor). Bin size of $\Delta d = 0.2$ was used to compute these $d_{\mathrm{LOS}}$ distributions. We focus on the peak of the distribution (discussed in \ref{sec:dlos}).} \label{fig:d_los}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fiber-collision Correction Method
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber-collision Correction Method} \label{sec:fc_corr}
To account for the systematic effects of fiber-collisions \cite{Anderson:2012aa}, for the BOSS galaxy data, most recently used a nearest-neighbor galaxy weighting scheme. For galaxies without resolved spectroscopic redshifts due to fiber-collisions, the entire statistical weight of the galaxy was assigned to its nearest-neighbor. This method assumes that all galaxies with angular separations $< 62 "$ are correlated. In other words, that galaxies within the fiber-collision angular scale reside in the same group or cluster. Consequently, galaxies that have angular separations $< 62"$ purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated and displaced significantly from its true position. Even for fiber-collided galaxies that reside in the same group or cluster, upweighting the nearest neighbor ignores halo-scale line-of-sight displacements.

While the nearest-neighbor method provides a reasonable estimate at large scales, in Section \ref{sec:dlos} we demonstrate that at small scales it's effects on the power spectrum are significant and outweigh sample variance. Furthermore, in Section \ref{sec:dlos}, we present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between close galaxy pairs. Then in Section \ref{sec:shotnoise}, we present corrections to the power spectrum estimator that further accounts for fiber-collisions through the shot-noise correction term in the estimator.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LOS DISPLACEMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Line-of-Sight Displacement of Fiber-collided Pairs} \label{sec:dlos}
It is impossible to determine in observed galaxy data whether fiber-collided galaxies without resolved spectroscopic redshift are either correlated or chance alignments. Fortunately, using just the close galaxy pairs with resolved redshifts (especially in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the fraction of galaxy pairs that are corrected and uncorrelated.

Meanwhile, for simulated mock catalogues, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a trivial task since fiber-collisions are post-processed after the simulated galaxy positions are generated. Hence all redshift values are resolved regardless of angular proximity. With both redshifts of the fiber-collided pair galaxies, we are able to emulate the observed data by assigning nearest neighbor galaxy weights (as done in \citealt{Anderson:2012aa}). So for a close galaxy pair, one galaxy (``the nearest neighbor") will have the statistical weight of both galaxies, while the other has a statistical weight of $0$. Furthermore, having the redshift values of close galaxy pairs in mock catalogues, allows us to model the correlated and uncorrelated fiber-collided pairs.

@@

After calculating the $d_{\mathrm{LOS}}$ for each of the fiber-collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor). All of the $d_{\mathrm{LOS}}$ distributions contain two distinct components: a peak approximately within the range $-10\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 10\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) that extends to $d_{\mathrm{LOS}}$ that encompasses the survey depth (entire range of the distribution not displayed in Figure \ref{fig:d_los}). We note that for the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber-collided pairs without resolved spectra, the $d_\mathrm{LOS}$ distribution represents the $d_\mathrm{LOS}$ from close galaxy pairs with resolved spectroscopic redshifts, often from overlapping regions of the BOSS survey.

Galaxies that are in the same groups or clusters, due to their gravitational interactions at halo-scales, are more likely to be in close angular proximity with each other. These galaxies in over-dense regions cause the peak in the $d_{\mathrm{LOS}}$ distribution. While the ``tail" component is composed of galaxy pairs that are arbitrarily in close angular proximity even when they are not correlated.

Focusing on the peak of the distribution, we note that it closely traces an exponential function. Therefore, we fit an exponential of the form, 
\begin{equation} \label{eq:peak} 
p(d_{\mathrm{LOS}}) = A \; e^{-|d_{\mathrm{LOS}}|/\sigma}
\end{equation}
 for a mathematical prescription of the $d_{\mathrm{LOS}}$ distribution peak as a function of the displacement for each of the data catalogues in Figure \ref{fig:d_los}. The best-fit $\sigma$ and $A$ parameters are obtained by fitting Equation \ref{eq:peak} to the $d_{\mathrm{LOS}}$ distribution peaks using MPFIT (\citealt{Markwardt:2009aa}). We list the values of $\sigma$ obtained for the mock catalogues in Table \ref{tab:mpfit}. Both Table \ref{tab:mpfit} and Figure \ref{fig:d_los} illustrate that the $d_{\mathrm{LOS}}$ distributions for the mock catalogues closely trace the distribution of the BOSS DR12, which further goes to support our use of mock catalogues to test our fiber-collision correction method.

 \begin{table} 
 \caption{$d_{\mathrm{LOS}}$ Distribution Best-fit Parameters} \label{tab:mpfit}
 \begin{spacing}{1.5}
 \begin{center}
 \leavevmode
 \begin{tabular}{ccc} \hline \hline
Catalogue &$\sigma$ ($h^{-1}\mathrm{Mpc}$) & $f_{\mathrm{peak}}$\\ \hline
Las Damas 	& 6.85	& 0.71 \\ 
QPM 		& 4.98	& 0.65 \\ 
Tiling Mock 	& 5.38	& 0.57 \\ 
BOSS DR12 	& 7.6		& 0.65 \\ \hline
\end{tabular} \par
\end{center}
\end{spacing}
%    \bigskip 
{\bf Notes}: Best-fit parameter $\sigma$ and peak fraction $f_{\mathrm{peak}}$ for the $d_{\mathrm{LOS}}$ distributions in Figure \ref{fig:d_los}. 
\end{table}

Using the exponential fits to the peak of the $d_{\mathrm{LOS}}$ distribution, we can also estimate the fraction of fiber-collided pairs that are within the peak: 
\begin{equation}
f_{\mathrm{peak}} = \frac{\sum\limits_{\mathrm{peak}} p(d_{\mathrm{LOS}})}{N_{\mathrm{pairs}}}, 
\end{equation}
where $N_{\mathrm{pairs}}$ is the total number of fiber-collided pairs. As mentioned above, this portion of fiber-collided pairs are galaxy pairs that are correlated. We list the $f_{\mathrm{peak}}$ values for each of the data catalogues in Table \ref{tab:mpfit}. The $f_\mathrm{peak}$ values for the mock catalogue are also in good agreement with the BOSS DR12 $f_\mathrm{peak}$.

As stated earlier, the current method of accounting for fiber-collisions uses the nearest-neighbor upweighting scheme (hereafter NN-upweighting). For this method to be completely correct, the $d_{\mathrm{LOS}}$ distribution would have to be a delta function, which as Figure \ref{fig:d_los} demonstrates is not the case. By simply incorporating the peak of the $d_{\mathrm{LOS}}$ distribution, we are able to significantly improve clustering statistics on small scales. Rather than placing the fiber-collided galaxy on top of its nearest neighbor, as NN-upweighting does, placing the fiber-collided galaxy at displacement sampled from the $d_{\mathrm{LOS}}$ distribution, away from the nearest neighbor better accounts for the small scale clustering measurements. On mock catalogues, we test this by first applying the NN upweighting in the same way as it is applied in the BOSS DR12 catalogue to the mock catalogues. We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber-collided pair. Afterwards we ``place" the fiber-collided galaxy a distance $d_i$ from the upweighted galaxy and reduce the statistical weight of the upweighted galaxy (the nearest-neighbor) by 1. We refer to this method as ``$d_\mathrm{LOS}$-peak.

\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
\caption{The ratio of $P(k)$ using the nearest-neighbor upweighting (blue) and $d_\mathrm{LOS}$ distribution peak fiber-collision correction (orange) over the true $P(k)$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues. }\label{fig:peakonly}
\end{center}
\end{figure*}

The $d_\mathrm{LOS}$-peak correction method is only part of our correction scheme we present in this paper. Nonetheless, we test it by applying it to the mock catalogues and comparing the resulting power spectrums. For each of the mock catalogues (Las Damas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from before to compute the power spectrums of the original mock data, the mock data with NN-upweighting, and the mock data with the $d_\mathrm{LOS}$-peak correction. We note that both the NN-upweighting and the $d_\mathrm{LOS}$-peak correction methods alter the redshift distribution of our samples by a negligible amount $< 1\%$. Therefore, the synthetic random catalogues and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations.

Since we are interested in how well these fiber-collision considerations can reproduce the power spectrum without fiber collisions (the ``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $P(k)$ computed from corrected mock catalogues over the average $P(k)$ from the original mock catalogues, $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$. The ratio for the NN upweighting scheme is plotted in blue while the ratio for the $d_{\mathrm{LOS}}$-peak correction scheme is plotted in orange. Also plotted is $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) in order to compare the ratios to sample variance of the mock catalogues. For all mocks, the $P(k)$ from the NN upweighting scheme is greater than $P_\mathrm{true}(k)$ by $> 10 \%$ at $ k \sim 0.3\; h/\mathrm{Mpc}$. In comparison, $P(k)$ from the $d_\mathrm{LOS}$-peak correction method is $\sim 5\%$ greater than $P_\mathrm{true}(k)$ - a significant improvement.

Comparing the NN-upweighting and the $d_\mathrm{LOS}$-peak methods to the sample variance ($\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$), reveal that neither of these methods provide a sufficient correction for the fiber-collision at $k > 0.1\; h/\mathrm{Mpc}$. The $P(k)$s obtained from these methods are dominated by systematics on small scales. Furthermore, the $d_\mathrm{LOS}$-peak method only statistically accounts for correlated pairs and does not consider uncorrelated pairs. Using the entire $d_\mathrm{LOS}$ distribution in order to account for uncorrelated pairs results in an overall reduction of $P(k)$ since the method displaces some close pairs that are actually correlated pairs as uncorrelated pairs and the other way around. Therefore, a more robust fiber-collision correction method is required. 
%detailed examination of peak only figure

>>>>

\section{Introduction} 
Through the millions of redshifts obtained through redshift surveys, cosmological measurements such as galaxy clustering statistics are no longer dominated by uncertainties from statistical precision, but from systematic effects of the measurements. These redshift surveys, such as the 2dF Galaxy Redshift Survey (2dFGRS; \citealt{Colless:1999aa}) and the Sloan Digital Sky Survey-III Baryon Oscillation Spectroscopic Survey (SDSS-III BOSS; \citealt{Anderson:2012aa, Dawson:2013aa}) and future redshift surveys such as the Extended Baryon Oscillation Spectroscopic Survey (eBOSS; {\bf WHO DO CITE?}) use fiber fed spectrographs.

@@

In Figure \ref{fig:zdist}, we plot the redshift distribution for LasDamas, QPM, and Tiling Mock catalogues along with the redshift distribution of BOSS DR12 galaxies. The LasDamas mock catalogue, which is modeled after the SDSS LRG sample has a constant $\bar{n}(z)$ over the redshift $0.16 < z< 0.44$, while the QPM and Tiling mock redshift distributions closely trace the observed BOSS redshift distribution (roughly $0.43 < z < 0.7$).

\subsection{Power Spectrum Estimator} 
In this paper, we focus on the effects of fiber-collisions on the galaxy power spectrum out of the various clustering measurements. Throughout the paper, when we measure the power spectrum, we use the standard \cite{Feldman:1994aa} (hereafter FKP) estimator and the following formalisms from the FKP paper: 
\begin{equation} \label{eq:fkppk}
P({\bf k}) = <|F({\bf k})|^2> - \frac{(1+\alpha) \int d^3r \;\bar{n}({\bf r})w_{\mathrm{FKP}}^2({\bf r})} {\int d^3r \; \bar{n}^2({\bf r})w_{\mathrm{FKP}}^2({\bf r})},
\end{equation}  
where
\begin{equation}
F({\bf r}) = \frac{w_\mathrm{FKP}({\bf r}) [n_g({\bf r}) - \alpha n_r({\bf r})]} {[\int d^3r \; \bar{n}^2({\bf r})w_\mathrm{FKP}^2({\bf r})]^{\frac{1}{2}}} 
\end{equation}
and the second term represents the constant shot-noise contribution to the power due to the discrete density field of our galaxies. $n_g$ is the galaxy density, $n_r$ is the density of the synthetic random catalogue, $\alpha$ is the ratio of the number of galaxies over the number of synthetic random galaxies, $\bar{n}$ is the mean density of the galaxies, and $w_{\mathrm{FKP}}$ is the minimum variance weight derived in \cite{Feldman:1994aa}: 
\begin{equation}
w_{\mathrm{FKP}} ({\bf r}) = \frac{1}{1+\bar{n}({\bf r}) P_0}
\end{equation}
where $P_0$ is the power spectrum amplitude at which the error is minimized. We use $P_0 = 20000\; \mathrm{Mpc}^3/h^3$ for our analysis, which corresponds to $k \sim 0.1\; h/\mathrm{Mpc}$.

@@

For LasDamas, QPM, and Tiling mock catalogues we use the FKP estimator described above to measure the power spectrum in Figure \ref{fig:mockpk}. The fiber-collisions described in Section \ref{sec:catalog} are not applied to the mock catalogues used to calculated the $P(k)$ in Figure \ref{fig:mockpk}. Without fiber-collisions, we are able to use the exact formulation of Equation \ref{eq:fkppk} in the FKP $P(k)$ estimator.

For the BOSS Data Release 12 $P(k)$ (\cmasscolor) in Figure \ref{fig:mockpk}, systematic weights are assigned to the galaxies in order to account for sector completeness, redshift failures, and fiber-collisions. Each galaxy has a statistical weight determined by, 
\begin{equation} \label{eq:weight}
w_\mathrm{tot} = w_\mathrm{sys} (w_\mathrm{rf} + w_\mathrm{fc} -1), 
\end{equation} 
(\citealt{Anderson:2012aa, Beutler:2014aa}). As a result, we modify Equation \ref{eq:fkppk} to obtain the power spectrum. Instead of the galaxy density term $n_g({\bf r})$ we use a weighted galaxy density term $n'_g({\bf r}) = n_g({\bf r}) w({\bf r})$, which includes the systematic weights for each galaxy. Also, instead of $\alpha = N_{\mathrm{gal}}/N_\mathrm{ran}$ we use $\alpha ' = N'_\mathrm{gal}/N_\mathrm{ran}$ where $N'_\mathrm{gal} = \sum_\mathrm{gal} w_\mathrm{tot}$.

For LasDamas and QPM, which have multiple realizations, we compute the sample variance of the power spectrum
\begin{equation} \label{eq:pk_var}
\Delta P (k)= \sqrt{\frac{1}{N_\mathrm{realization}} \sum\limits_i^{N_\mathrm{realization}} (P_i(k)- \overline{P(k)})^2 }. 
\end{equation}
$N_\mathrm{realization}$ is the total number of realizations (40 for LasDamas and 1000 for QPM) and $P_i(k)$ is the power spectrum for each realization. $\Delta P(k)$ is represented by the width of the $P(k)$ in Figure \ref{fig:mockpk}.

\begin{figure*}
\begin{center}
\includegraphics[scale=0.575]{fcpaper_dlos_dist.png}
\caption{Normalized distribution of $d_{\mathrm{LOS}}$ for Las Damas (\ldgcolor), QPM (\qpmcolor), and Tiling Mock (\tmcolor) mock catalogues. The normalized $d_{\mathrm{LOS}}$ distribution of BOSS DR12 is also plotted (\cmasscolor). Bin size of $\Delta d = 0.2$ was used to compute these $d_{\mathrm{LOS}}$ distributions. Although we focus on the peak of the distribution (discussed in \ref{sec:dlos}), the $d_\mathrm{LOS}$ distribution extends to $\sim \pm 500 \; \mathrm{Mpc}$ (not shown above).} \label{fig:d_los}
% perhaps the range should be wider and make it full text width that way the tail can be portrayed better. Keep the same aspect ratio. 
\end{center}
\end{figure*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Fiber-collision Correction Method
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fiber-collision Correction Method} \label{sec:fc_corr}
As mentioned above, a common approach in accounting for fiber-collisions in clustering measurements has been to use the nearest angular neighbor method (\citealt{Zehavi:2002aa, Berlind:2006aa, Anderson:2012aa}). For galaxies without resolved spectroscopic redshifts due to fiber-collisions, the entire statistical weight of the galaxy is assigned to its nearest angular neighbor. This method assumes that all galaxies with angular fiber-collision scale ($< 62 "$ for BOSS) are correlated. In other words, the method assumes that galaxies within the fiber-collision angular scale reside in the same halo. Consequently, galaxies within the angular fiber-collision scale purely by coincidence (hereafter referred to as ``chance alignments") are incorrectly assumed to be gravitationally correlated, so when their statistical weight is added to its nearest angular neighbor, they are in fact displaced significantly from its true position. For BOSS, the nearest angular neighbor method can displace galaxies by up to $500 \;\mathrm{Mpc}$. Even for fiber-collided galaxies that reside in the same group or cluster, upweighting the nearest neighbor ignores halo-scale line-of-sight displacements and places the fiber-collided galaxies on top of each other.

Although the nearest-neighbor method provides a reasonable estimate at large scales, as we demonstrate in Section \ref{sec:dlos}, at small scales its effects on the power spectrum are significant and dominate sample variance. Afterwards, in Section \ref{sec:dlos}, we present an improved method to account for correlated fiber-collided galaxies using the line-of-sight displacement between close galaxy pairs. Then in Section \ref{sec:shotnoise}, we present adjustments to the FKP power spectrum estimator that properly accounts for fiber-collisions through the shot-noise correction term in the estimator.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% LOS DISPLACEMENT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Line-of-Sight Displacement of Fiber-collided Pairs} \label{sec:dlos}
It is impossible to determine in observed galaxy data whether fiber-collided galaxies without resolved spectroscopic redshift are either correlated or chance alignments. Fortunately, using the close galaxy pairs with resolved redshifts (mainly in the overlapping regions mentioned in Section \ref{sec:catalog}), it is possible to model the fraction of galaxy pairs that are corrected and uncorrelated.

Meanwhile, for simulated mock catalogues, described in Section \ref{sec:catalog}, modeling the fiber-collided galaxy pairs is a much more direct task since fiber-collisions are post-processed after the simulated galaxy positions are generated. Hence all redshift values are resolved regardless of angular proximity. With both redshifts of the fiber-collided pair galaxies, the fiber-collisions we impose, or are already imposed, on the mock catalogues in Section \ref{sec:catalog} emulate the observed data by assigning nearest neighbor galaxy weights. So for a close galaxy pair, one galaxy (``the nearest neighbor") will have the statistical weight of both galaxies, while the other has a statistical weight of $0$. Furthermore, having the redshift values of close galaxy pairs in mock catalogues, allows us to model the correlated and uncorrelated fiber-collided pairs.

@@

After calculating the $d_{\mathrm{LOS}}$ for every fiber-collided pairs, in Figure \ref{fig:d_los} we present the distribution of $d_{\mathrm{LOS}}$ for LasDamas (\ldgcolor), QPM (\qpmcolor), Tiling Mock (\tmcolor), and BOSS DR12 (\cmasscolor). All of the $d_{\mathrm{LOS}}$ distributions contain two components: a peak contained within the range $-20\;\mathrm{Mpc} < d_{\mathrm{LOS}} < 20\;\mathrm{Mpc}$ and a flat component (hereafter "tail" component) outside the peak that extends to $d_{\mathrm{LOS}} \sim \pm 500 \;\mathrm{Mpc}$ (entire range of the distribution not displayed in Figure \ref{fig:d_los}). For the BOSS data, since we cannot compute the $d_\mathrm{LOS}$ for fiber-collided pairs without resolved spectra, the $d_\mathrm{LOS}$ distribution only reflects the $d_\mathrm{LOS}$ from fiber-colldied pairs {\em with} resolved spectroscopic redshifts, mostly from tile overlapping regions of the BOSS survey.

Galaxies within the same halo, due to their gravitational interactions at halo-scales, are more likely to be in close angular proximity with each other. These galaxies in over-dense regions cause the peak in the $d_{\mathrm{LOS}}$ distribution. While the ``tail" component is composed of chance alignment galaxy pairs that are arbitrarily in close angular proximity even when they are not correlated.

Focusing on the peak of the distribution, we note that it closely traces an Gaussian function. Therefore, we fit a Gaussian of the form, 
\begin{equation} \label{eq:peak} 
p(d_{\mathrm{LOS}}) = A \; e^{-{d_{\mathrm{LOS}}^2}/{2\sigma^2}}
\end{equation}
 for a mathematical prescription of the $d_{\mathrm{LOS}}$ distribution peak as a function of the displacement for each of the data catalogues in Figure \ref{fig:d_los}. The best-fit $\sigma$ and $A$ parameters are obtained by fitting Equation \ref{eq:peak} to the $d_{\mathrm{LOS}}$ distribution peaks using MPFIT (\citealt{Markwardt:2009aa}). We list the values of $\sigma$ obtained for the mock catalogues in Table \ref{tab:mpfit}. Both Table \ref{tab:mpfit} and Figure \ref{fig:d_los} illustrate that the $d_{\mathrm{LOS}}$ distributions for the mock catalogues closely trace the distribution of the BOSS DR12, which further goes to support the use of mock catalogues in our investigation of fiber-collisions.

 \begin{table} 
 \caption{$d_{\mathrm{LOS}}$ Distribution Best-fit Parameters} \label{tab:mpfit}
 \begin{spacing}{1.5}
 \begin{center}
 \leavevmode
 \begin{tabular}{ccc} \hline \hline
Catalogue &$\sigma$ ($\mathrm{Mpc}$) & $f_{\mathrm{peak}}$\\ \hline
Las Damas 	& 6.85	& 0.71 \\ 
QPM 		& 4.98	& 0.65 \\ 
Tiling Mock 	& 5.38	& 0.57 \\ 
BOSS DR12 	& 7.6		& 0.65 \\ \hline
\end{tabular} \par
\end{center}
\end{spacing}
%    \bigskip 
{\bf Notes}: Best-fit parameter $\sigma$ and peak fraction $f_{\mathrm{peak}}$ for the $d_{\mathrm{LOS}}$ distributions in Figure \ref{fig:d_los}. 
\end{table}

Using the best-fit to the peak of the $d_{\mathrm{LOS}}$ distribution, we estimate the fraction of fiber-collided pairs that are within the peak: 
\begin{equation}
f_{\mathrm{peak}} = \frac{\sum\limits_{\mathrm{peak}} p(d_{\mathrm{LOS}})}{N_{\mathrm{pairs}}}, 
\end{equation}
where $N_{\mathrm{pairs}}$ is the total number of fiber-collided pairs. As mentioned above, this portion of fiber-collided pairs are galaxy pairs that are correlated. We list the $f_{\mathrm{peak}}$ values for each of the data catalogues in Table \ref{tab:mpfit}. The $f_\mathrm{peak}$ values for the mock catalogue are also in good agreement with the BOSS DR12 $f_\mathrm{peak}$.

For the most commonly used nearest angular neighbor method (hereafter NN) to be completely correct, the $d_{\mathrm{LOS}}$ distribution in Figure \ref{fig:d_los} would have to be a delta function, which is clearly not the case. By simply incorporating the peak of the $d_{\mathrm{LOS}}$ distribution, we are able to significantly improve clustering statistics on small scales. Rather than placing the fiber-collided galaxy on top of its nearest angular neighbor as NN does, placing the fiber-collided galaxy at a displacement sampled from the $d_{\mathrm{LOS}}$ distribution, away from its nearest neighbor better accounts for the small scale in clustering measurements. On mock catalogues, we test this by first applying the NN to the mock catalogues. We then sample a displacement $d_i$ from $p(d_\mathrm{LOS})$ (Equation \ref{eq:peak}) for each fiber-collided pair. Afterwards we ``place" the fiber-collided galaxy a distance $d_i$ from the nearest neighbor galaxy and reduce the statistical weight of the the nearest-neighbor by 1. We refer to this method as ``$d_\mathrm{LOS}$-peak".

\begin{figure*}
\begin{center}
\includegraphics[scale=0.55]{fcpaper_pk_peakonly_comp.png} 
\caption{The ratio of $\overline{P(k)}$ using the nearest-neighbor (NN) correction (blue) and $d_\mathrm{LOS}$-peak correction (orange) over the true $\overline{P(k)}$ for LasDamas (left panel), QPM (middle panel), and Tiling Mock (right panel) catalogues. The ratio of the sample variance to the true $\overline{P(k)}$, $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed), is plotted for comparison. The NN correction and $d_\mathrm{LOS}$-peak correction methods are described in Section \ref{sec:dlos}. Incorporating the $d_{\mathrm{LOS}}$ distribution significantly improves the correction of fiber-collisions; however, both methods dominate the sample variance at $k > 0.3 \; h/\mathrm{Mpc}$.}\label{fig:peakonly}
\end{center}
\end{figure*}

The $d_\mathrm{LOS}$-peak correction is the first part of our correction method we present in this paper. Nonetheless, we test it by applying it to the mock catalogues and comparing the resulting power spectrums. For each of the mock catalogues (Las Damas, QPM, and Tiling Mock) we use the FKP power spectrum estimator from before to compute the power spectrums of the original mock data, the mock data with the NN correction, and the mock data with the $d_\mathrm{LOS}$-peak correction. We note that both the NN and the $d_\mathrm{LOS}$-peak correction methods alter the redshift distribution of our samples by a negligible amount $< 1\%$. Therefore, the synthetic random catalogues and the $\bar{n}(z)$ values do not need to be adjusted in the FKP $P(k)$ calculations.

Since we are interested in how well fiber-collision correction methods can reproduce the power spectrum without fiber collisions (i.e. ``true" power spectrum, unsullied by systematic effects), in Figure \ref{fig:peakonly} we plot the ratio of the average power spectrum $\overline{P(k)}$ (averaged over the realizations) computed from corrected mock catalogues over the $\overline{P(k)}$ from the original mock catalogues: $\overline{P_{\mathrm{corr}}(k)}/\overline{P_\mathrm{true}(k)}$. The ratio for the NN method is plotted in blue while the ratio for the $d_{\mathrm{LOS}}$-peak correction is plotted in orange. We also plot $\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$ (black; dashed) in order to compare the ratios to sample variance of the mock catalogues. 
At large scales ($k < 0.1 \; h/\mathrm{Mpc}$), for all mock catalogues, both fiber-collision methods are able to reasonably reconstruct the true power spectrum. At small scales on the other than, the NN corrected $\overline{P(k)}$ is greater than $\overline{P_\mathrm{true}(k)}$ by $> 10 \%$ at $ k \sim 0.3\; h/\mathrm{Mpc}$. In comparison, the $d_\mathrm{LOS}$-peak corrected $\overline{P(k)}$ is $\sim 5\%$ greater than $P_\mathrm{true}(k)$ at $k \sim 0.3 \; h/\mathrm{Mpc}$ - a significant improvement. {\bf include more description of even smaller scales when the figures are ready}.

Comparing the NN method and the $d_\mathrm{LOS}$-peak correction to the sample variance ratio ($\Delta P_\mathrm{true}(k) / \overline{P_\mathrm{true}(k)}$), reveal that neither of these methods sufficiently correct for fiber-collision at $k > 0.1\; h/\mathrm{Mpc}$. The $P(k)$s obtained from these methods are clearly dominated by the systematic effects of fiber-collisions on small scales. Although the $d_\mathrm{LOS}$-peak method we propose provides an improvement from the NN method through our statistical treatment of correlated pairs within the peak of the $d_\mathrm{LOS}$ distribution, there is still room for improvement since it does not properly account for chance alignments (uncorrelated fiber-collision pairs). Unfortunately, an extension of the $d_\mathrm{LOS}$-peak method to the entire $d_\mathrm{LOS}$ distribution range is not feasible is not feasible because such a correction results in an overall reduction of the $P(k)$. This is caused by the statistical sampling of the $d_\mathrm{LOS}$, which displaces fiber-collided pairs that are actually correlated pairs as chance alignments and the other way around. Therefore, in the following section we provide more robust correction method to account for the chance alignment fiber-collided pairs.
